---
title: "Coral Reef Gender & Diversity Analysis"
author: "Sam Cheng"
date: "01/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)
library(tm)
library(maptools)
library(rgdal)
library(broom)
library(mapproj)
library(viridis)
library(knitr)
library(scales)
library(cowplot)
```

## Introduction

The goal of this project is to examine patterns in author diversity (gender/geographic) in coral reef publications over the past 15 years. We selected a range of peer-reviewed scientific journals across different impact factors and levels (incl. Conservation Letters, PNAS, Proceedings of the Royal Society B, Coral Reefs, PlosOne, Marine Policy, Marine Biology, Frontiers in Marine Science, Nature, Science). A team of global coral reef scientists reviewed these articles and extracted relevant data on research area, geography, authorship, and gender.

<span style="color: purple;">
**Notes for co-authors to consider are in bold purple**
</span>

```{r data, include=FALSE}
data <- read.csv("coralreef_gender_cleaned_final_2020.csv",header=TRUE)
data <- data %>% filter(is.na(Excluded)) %>% distinct()
data <- filter(data,!is.na(Pub_year))

##Coding first and last authors
id <- unique(data$Article.ID)
x <- c(1:n_distinct(data$Article.ID))
first_last <- data.frame(Article.ID=integer(),Author_order=integer(),First_last=character())

dat <- data %>% select(Article.ID, Author_order) %>% distinct()

for (i in x){
  y <- id[i]
  sub <- dat %>% filter(Article.ID == y) %>% distinct()
  z <- c(1:nrow(sub))
  l <- max(sub$Author_order)
  if(length(z) == 1){
    sub[1,3] <- c("single")
  } else {
    for(i in z){
      if (sub[i,2] == 1) {
        sub[i,3] <- c("first")
      } else if (sub[i,2] == l) {
        sub[i,3] <- c("last")
      } else {
        sub[i,3] <- c("other")
      }
    }
  }
  first_last <- rbind(first_last,sub)
}

colnames(first_last) <- c("Article.ID","Author_order","First_last")

df <- left_join(data,first_last,by=c("Article.ID","Author_order"))
df$Study.Country <- as.character(df$Study.Country)

#Separating out countries for stats and mapping
df_c <- select(df, Article.ID, Study.Country) %>% distinct()
df_c <- df_c %>% filter(!is.na(Study.Country)) %>% distinct()

#Fix syntax and delimiter between countries, fixing mispellings and typos
df_c$Study.Country <- gsub(', ',',',df_c$Study.Country)
df_c$Study.Country <- gsub('Congo,The Democratic Republic Of The','Congo, The Democratic Republic Of',df_c$Study.Country)
df_c$Study.Country <- gsub('Congo,The Democratic Republic Of','Congo, The Democratic Republic Of',df_c$Study.Country)
df_c$Study.Country <- gsub('Iran,Islamic Republic Of','Iran, Islamic Republic Of',df_c$Study.Country)
df_c$Study.Country <- gsub('Korea,South','Republic of Korea',df_c$Study.Country)
df_c$Study.Country <- gsub('Korea,North',"Korea, The Democratic People's Republic Of",df_c$Study.Country)
df_c$Study.Country <- gsub('Micronesia,Federated States of','Micronesia, Federated States of',df_c$Study.Country)
df_c$Study.Country <- gsub('Taiwan,Province Of China','Taiwan, Province Of China',df_c$Study.Country)
df_c$Study.Country <- gsub('Tanzania,United Republic Of','Tanzania, United Republic Of',df_c$Study.Country)
df_c$Study.Country <- gsub(' US Virgin Islands','United States Virgin Islands',df_c$Study.Country)
df_c$Study.Country <- gsub('US Virgin Isands','United States Virgin Islands',df_c$Study.Country)
df_c$Study.Country <- gsub('US Virgin Islands','United States Virgin Islands',df_c$Study.Country)
df_c$Study.Country <- gsub('USA','United States',df_c$Study.Country)
df_c$Study.Country <- gsub(' Northern Mariana Islands','Northern Mariana Islands',df_c$Study.Country)
df_c$Study.Country <- gsub('Brazil ','Brazil',df_c$Study.Country)
df_c$Study.Country <- gsub('Cook Ilsands','Cook Islands',df_c$Study.Country)
df_c$Study.Country <- gsub("DRC", "Congo, The Democratic Republic Of", df_c$Study.Country)
df_c$Study.Country <- gsub("HI", "United States", df_c$Study.Country)
df_c$Study.Country <- gsub("imor Leste", "Timor-Leste", df_c$Study.Country)
df_c$Study.Country <- gsub("Chagos Archipelago","Chagos", df_c$Study.Country)
df_c$Study.Country <- gsub("New Calednoia","New Caledonia", df_c$Study.Country)
df_c$Study.Country <- gsub("Phillipines","Philippines", df_c$Study.Country)
df_c$Study.Country <- gsub("Pitcairn Islands","Pitcairn", df_c$Study.Country)
df_c$Study.Country <- gsub("St. Vincent","Saint Vincent", df_c$Study.Country)
df_c$Study.Country <- gsub("Saudia Arabia","Saudi Arabia", df_c$Study.Country)
df_c$Study.Country <- gsub("Saint Vincent And The Grenadines","Saint Vincent and the Grenadines", df_c$Study.Country)

df_c$Study.Country <- gsub('(\\w),(\\w)','\\1;\\2',df_c$Study.Country)

#Splitting countries out onto separate lines
c <- strsplit(df_c$Study.Country, split=";")
dataframe <- data.frame(ID=rep(df_c$Article.ID, sapply(c, length)), Study.Country = unlist(c))
colnames(dataframe) <- c("Article.ID","Study_Country")
dataframe <- distinct(dataframe)

#Add new column to dataframe
df2 <- left_join(df,dataframe,by="Article.ID") 

country.names <- df2 %>% select(Study_Country) %>% distinct() %>% filter(Study_Country != "") %>% filter(!is.na(Study_Country)) %>% distinct()  %>% arrange(Study_Country)

#Fixing regional/global
df2$Study_Country <- gsub('Global',NA,df2$Study_Country)
df2$Study_Country <- gsub('ABNJ',NA,df2$Study_Country)

#Creating new column for mapping purposes (territories without ISO 3166 codes are mapping under territory holder code), adjusting names to official "mapping" names
df2$Mapping_Country <- df2$Study_Country
df2$Mapping_Country <- gsub('Andaman and Nicobar','India',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Venezuela','Venezuela (Bolivarian Republic of)',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Wake Atoll','United States Minor Outlying Islands',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Swaziland','Eswatini',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Palmyra','United States Minor Outlying Islands',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Chagos Archipelago','British Indian Ocean Territory',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Saba','Bonaire, Sint Eustatius, Saba',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Bonaire','Bonaire, Sint Eustatius, Saba',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Scotland','United Kingdom',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Corsica (France)','France',df2$Mapping_Country)
df2$Mapping_Country <- gsub('Clipperton Atoll','United Kingdom',df2$Mapping_Country)

#Fixing study_type syntax
df_s <- select(df2, Article.ID, Laboratory) %>% distinct()
df_s <- df_s %>% filter(!is.na(Laboratory)) %>% distinct()

#Fix syntax and delimiter between countries, fixing mispellings and typos
df_s$Laboratory <- gsub(', ',',',df_s$Laboratory)
df_s$Laboratory <- gsub(',',';',df_s$Laboratory)
df_s$Laboratory <- gsub('; ',';',df_s$Laboratory)
df_s$Laboratory <- gsub('; ',';',df_s$Laboratory)
df_s$Laboratory <- gsub('Desk Studies','Desk studies',df_s$Laboratory)
df_s$Laboratory <- gsub('Field-based;Synthesis Modelling','Field-based;Synthesis;Modelling',df_s$Laboratory)
df_s$Laboratory <- gsub('Modeling','Modelling',df_s$Laboratory)
df_s$Laboratory[df_s$Laboratory == "Correspondence"] <- c("Editorials/Correspondence")
df_s$Laboratory[df_s$Laboratory == "Editorials"] <- c("Editorials/Correspondence")
df_s$Laboratory[df_s$Laboratory == ""] <- c("Undetermined")

#Splitting countries out onto separate lines
s <- strsplit(df_s$Laboratory, split=";")
dataframe_s <- data.frame(ID=rep(df_s$Article.ID, sapply(s, length)), Study_Type = unlist(s))
colnames(dataframe_s) <- c("Article.ID","Study_Type")
dataframe_s <- distinct(dataframe_s)

#Add new column to dataframe
df2 <- left_join(df2,dataframe_s,by="Article.ID") 

colnames(df2) <- c("Done","Excluded","Reviewer","Article.ID","Author","Author_gender","Country_affiliation","Title","Keywords","Abstract","Study.Country","Territory.disputed","Study_region","Study_type","Marine_realm","Author.Based.In.Country","Author.Based.In.Sovereign","Times.Cited","DOI","Affiliation","Journal","Author_order","Pub_year","First_last","Study_Country","Mapping_Country","Study_Type")
```

## Summary statistics

```{r include = FALSE}
n <- n_distinct(df2$Article.ID)
j <- unique(df2$Journal)
y <- c(min(df2$Pub_year):max(df2$Pub_year))
a <- unique(df2$Author)
c <- unique(df2$Country_affiliation)
```
This study considered ``r n`` unique studies published between ``r y[1]`` and ``r y[17]``.
This dataset represents works by ``r length(a)`` unique authors from ``r length(c)`` different countries 

<span style="color: purple;">
**The number of unique authors is going to be wrong as names were not standardized between databases). We need to decide whether we want to spend time cleaning this or not. Variations include Last,First; First Last; Last, First Initial**
</span>

```{r gg, fig.cap="**Figure 1.** Growth in coral reef publications over the last 15 years", echo=FALSE}
growth <- df2 %>% select(Article.ID,Pub_year) %>% distinct()
g <- count(growth,Pub_year)

gg <- ggplot(g, aes(Pub_year,n)) + 
  geom_col(fill="steelblue") +
  scale_x_continuous(breaks=seq(2003,2019,1), name="Publication year") +
  scale_y_continuous(breaks=seq(0,200,50), name="Number of articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1)
  )
  
plot(gg)
```
##Geographic distribution of research 

```{r cc, include=FALSE}
##Plot countries
#load in full country list
country <- read.csv("country_code_web.csv", head=TRUE, sep=",")
names(country) <- c("Study_country", "Code","Territory","Sovereignty")
country$Study_country <- as.character(country$Study_country)

##Count number of studies for all countries and arrange by region
country_count <- matrix(nrow=nrow(country), ncol=2)
rownames(country_count) <- country$Study_country
colnames(country_count) <- c("Study_country", "counts")

df_country <- df2 %>% select(Article.ID,Mapping_Country) %>% filter(!is.na(Mapping_Country)) %>% distinct()

#Calculate in for loop and write to blank matrix
for (c in country$Study_country){
  subset <- filter(df_country, Mapping_Country == c)
  country_count[c,1] <- c
  country_count[c,2] <- as.numeric(n_distinct(subset$Article.ID))
}
#Remove rownames and reformat data types
rownames(country_count) = NULL
country_count <- as.data.frame(country_count, stringsAsFactors=FALSE)
countries <- left_join(country,country_count,by="Study_country")

countries$counts <- as.numeric(countries$counts)
countries <- as.data.frame(countries)
countries_zero <- filter(countries, counts == 0)

countries <- arrange(countries,desc(counts))

map <- readShapeSpatial("TM_WORLD_BORDERS-0.3/TM_WORLD_BORDERS-0.3.shp")
map <- fortify(map, region="ISO3")

```
Research was conducted in ``r nrow(filter(countries, counts !=0 & Territory == "N"))+2`` countries and ``r nrow(filter(countries, counts !=0 & Territory == "Y"))`` territories. The most studied countries were Australia ``r countries[1,1]`` (n=``r countries[1,5]``) and ``r countries[2,1]`` (n=``r countries[2,5]``). 

```{r cc_plot, fig.cap="**Figure 2.** Geographic distribution of study countries", fig.height=7, fig.width=12, echo=FALSE}
cc <- ggplot() + 
  geom_map(data=countries, aes(map_id=Code, fill=counts),map=map) + 
  geom_map(data=countries_zero, aes(map_id=Code),fill="#f0f0f0",map=map) + 
  expand_limits(x=map$long,y=map$lat) + 
  theme(panel.background = element_rect(fill = "grey50", colour = "white"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  scale_fill_gradient2(low="#deebf7",mid="#9ecae1",high="#08519c",midpoint=(max(countries$counts)/2),limits=c(0,max(countries$counts)))

plot(cc)
```

**This one needs the legend to look nicer
```{r cc_plot_alt, fig.cap='**Figure 2 (alternate).** Geographic distribution of study countries with discrete breaks', fig.height=7, fig.width=12, echo=FALSE}
##Define custom breaks for choropleth map
##Define custom breaks for choropleth map
min <- min(countries$counts) 
max <- max(countries$counts)
pretty_breaks <- c(5,25,50,100,250)
brks <- c(min,pretty_breaks,max)
#labels <- c("1-5","6-25","26-50","51-100","101-250","251-459")
labels <- c()
for(i in 1:length(brks)){
  labels <- c(labels,round(brks[i + 1], 2))
}
labels <- labels[1:length(labels)-1]

countries$brks2 <- cut(countries$counts,
                      breaks=brks,
                      include.lowest=TRUE,
                      labels=labels)

brks_scale <- levels(countries$brks2)
labels_scale <- brks_scale

cc <- ggplot() + 
  geom_map(data=countries, aes(map_id=Code, fill=brks2),map=map) + 
  geom_map(data=countries_zero, aes(map_id=Code),fill="#f0f0f0",map=map) + 
  expand_limits(x=map$long,y=map$lat) + 
  theme(panel.background = element_rect(fill = "grey50", colour = "white"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  coord_equal() +
  theme(legend.position = "bottom")


cd <- cc +
  scale_fill_manual(
    values=(brewer.pal(7, "BuGn")[2:7]),
    breaks=brks_scale,
    name="Number of articles",
    drop=FALSE,
    labels=labels_scale,
    guide=guide_legend(
      direction="horizontal",
      #keyheight= unit(2, units="mm"),
      #keywidth = unit(70/length(labels), units="mm"),
      title.position = "top",
      title.hjust = 0.5,
      label.hjust = 1,
      nrow=1,
      byrow=T,
      reverse=F,
      label.position="bottom"
      )
    )

plot(cd)
```

```{r mar_region, include=FALSE}
#Plot marine realms
m_lyr <- readOGR(dsn="MEOW-TNC", layer="meow_ecos",verbose=FALSE)
m_lyr_fortified <- tidy(m_lyr,region="REALM")

##Plot countries
map_lyr <- readOGR(
  dsn="TM_WORLD_BORDERS-0.3",
  layer="TM_WORLD_BORDERS-0.3",
  verbose=FALSE
)

ggmap <- tidy(map_lyr,region="ISO3")

#Clean marine realm data
realm <- df2 %>% select(Article.ID,Marine_realm) %>% distinct() %>% filter(Marine_realm != "")
realm$Marine_realm <- gsub(", ",",", realm$Marine_realm)
realm$Marine_realm <- as.character(realm$Marine_realm)
m <- strsplit(realm$Marine_realm, split=",")
m_df <- data.frame(ID=rep(realm$Article.ID, sapply(m, length)), id = unlist(m))
colnames(m_df) <- c("Article.ID","id")
m_df <- distinct(m_df)

#Count studies per realm
marine_count <- count(m_df,id)
marine_count$id <- as.character(as.factor(marine_count$id))
marine_data <- m_lyr_fortified %>% left_join(marine_count, by="id")
marine_data$n[is.na(marine_data$n)] <- 0
marine_data_zero <- marine_data %>% filter(n == 0)
marine_data <- marine_data %>% filter(n != 0)

#Summarized in a table
marine_data_summary <- marine_data %>% select(id, n) %>% distinct() %>% arrange(desc(n))

```

```{r mar_region_plot, fig.cap='**Figure 3. Distribution of research effort over marine realms**', fig.height=7, fig.width=12, echo=FALSE, results='asis'}
ggplot() + 
  geom_polygon(data=marine_data, aes(fill=n,x=long,y=lat,group=group)) +
  geom_polygon(data=marine_data_zero, aes(x=long,y=lat,group=group), fill="#7c7c7c") +
  geom_polygon(data=ggmap, aes(x=long,y=lat,group=group), fill="#ffffff") +
  scale_fill_gradient2(low="#deebf7",mid="#9ecae1",high="#08519c") +
  theme_minimal() +
  theme(
    #text = element_text(family = "Ubuntu Regular", color = "#22211d"),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(color = "#ebebe5", size = 0.1),
    panel.grid.minor = element_blank(),
    plot.background = element_rect(fill = "#000000", color = NA), 
    panel.background = element_rect(fill = "#f5f5f2", color = NA), 
    legend.background = element_rect(fill = "#f5f5f2", color = NA),
    panel.border = element_blank()
  )

kable(marine_data_summary, caption="Total articles by marine realm")
```


## Research topics and study types

Research topics were wide-ranging.
```{r ta, include = FALSE}
#Create corpus of titles and abstracts
ta <- df2 %>% select(Article.ID,Title,Abstract) %>% distinct() %>% unite("Text",c("Title","Abstract"),sep="; ")
text <- ta$Text
docs <- Corpus(VectorSource(text))
#Clean corpus
docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("coral","corals","reefs","reef"))

#Create document-term-matrix
dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
wc <- data.frame(word = names(words),freq=words)
```

```{r ta_plot, fig.cap='**Figure X.** Wordcloud of frequent words appearing in titles and abstracts', echo=FALSE}
#Generate word cloud
set.seed(1234) 
wordcloud(words = wc$word, freq = wc$freq, min.freq = 10,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"), scale=c(2.5,0.25))

```

```{r st, include=FALSE, echo=FALSE}
###Types of studies
##What study types are encountered?
type <- df2 %>% select(Article.ID,Study_Type) %>% distinct()
type_count <- count(type,Study_Type) %>% arrange(desc(n))

st <- ggplot(type_count, aes(Study_Type,n)) + 
  geom_col(fill="steelblue") +
  scale_y_continuous(breaks=seq(0,1100,100), name="Number of articles") +
  xlab("Study type") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1)
  )

plot(st)
```

## Author characteristics (gender, diversity)

```{r gender, include=FALSE}
##Cleaning data
gender <- df2 %>% select(-Done,-Excluded,-Reviewer,-Title,-Keywords,-Abstract,-DOI,-Affiliation,-Study_type,-Study.Country) %>% distinct()
gender$Author_gender <- gsub("FEmale","Female",gender$Author_gender)
gender$Author_gender <- gsub("Female ","Female",gender$Author_gender)
gender$Author_gender <- gsub("Male ","Male",gender$Author_gender)

#Assuming that unknown code implies undetermined
gender$Author_gender[gender$Author_gender == "Unknown"] <- "Undetermined"
gender$Author_gender[gender$Author_gender == ""] <- "Undetermined"
gender$Author_gender[is.na(gender$Author_gender)] <- "Undetermined"

#Percent authors successfully identified and summary stats
authors <- gender %>% select(Author_gender,Author) %>% distinct()

n_a <- n_distinct(authors$Author)
gender_stats <- count(authors,Author_gender)
```

This study found a maximum of ``r n_a`` unique authors in the evidence base. This number represents the maximum number of authors as different publication databases listed authors in different formats and thus we were unable to de-duplicate entries that were not an exact match (e.g. Last Name, First Name vs. Last Name, First Initial). ``r gender_stats[3,2]`` authors could not be located on the internet to confirm gender identity. Authors whose gender identity could not be reliably determined based on the presence of identified pronouns, declarations, or author(s) knowledge - were coded as "undetermined." The majority of authors in coral reef science are male.

```{r gender_stats, fig.cap='**Figure X.** Gender distribution of authors in coral reef science', fig.width=5, echo=FALSE}
gs_plot <- filter(gender_stats,Author_gender != "Not found")
gs <- ggplot(gs_plot, aes(x="",y=n,fill=Author_gender)) +
  geom_bar(width=1, stat="identity") +
  scale_fill_brewer(palette="Accent") +
  theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid = element_blank(),
    legend.position='bottom') +
  geom_text(aes(y=n, label=percent(n/n_a)), size=3, position=position_stack(vjust=0.5)) +
  ylab("Number of authors") +
  guides(fill=guide_legend(title="Gender"))

plot(gs)
```


```{r gender_position, fig.cap='**Figure X.** Frequency of male vs. female authors in first, last, and all other author positions', echo=FALSE}
ratio <- gender %>% select(Article.ID,Author_gender,First_last) %>% distinct()
x <- n_distinct(ratio$Article.ID)
rg <- count(ratio,Author_gender,First_last) %>% filter(First_last != "other")

ggplot(rg, aes(x=First_last,y=n)) +
  geom_bar(aes(fill=Author_gender), stat="identity", position=position_dodge()) + 
  scale_fill_brewer(palette="Accent") +
  theme_minimal() +
  theme(
    axis.ticks.x = element_blank(),
    legend.position='right') +
  ylab("Number of articles") +
  xlab("Author position") +
  guides(fill=guide_legend(title="Gender"))
```


```{r gender_time, fig.cap='**Figure X.** Change in proportion of genders in first, last, and single author positions over time', echo=FALSE}
gender_time <- gender %>% select(Article.ID,Author_gender,First_last,Pub_year) %>% filter(First_last != "other") %>% filter(Author_gender != "Undetermined") %>% filter(Author_gender != "Not found") %>% distinct() %>% group_by(Pub_year,First_last)
gt <- count(gender_time,Author_gender,First_last)

ggplot(gt, aes(Pub_year,n)) + 
  geom_col(aes(fill=Author_gender)) +
  facet_grid(rows=vars(First_last), scales="free") +
  scale_x_continuous(breaks=seq(2003,2019,1), name="Publication year") +
  scale_y_continuous(breaks=seq(0,200,50), name="Number of articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1)
  ) +
  theme(
    legend.position='bottom') +
  ylab("Number of articles") +
  xlab("Author position") +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))
```

Proportion of each gender's output was calculated by comparing the proportion of identified authorships for each gender in a given article. For example, if a paper had 9 authors, of which 8 were identified to gender, each authorship was granted an equal share of authorship (1/8 each). These fractions were then aggregated at different levels (e.g. countries, study_types, journals) to explore gender contributions. These reflect authorships and not individuals.

```{r gender_proportion, include=FALSE}
##Gender proportions per paper and aggregate
gender_prop <- gender %>% select(Article.ID, Author_gender,Author_order) %>% distinct()

```