---
title: "Coral Reef Gender & Diversity Analysis"
author: "Sam Cheng"
date: "01/18/2020"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)
library(tm)
library(maptools)
library(rgdal)
library(broom)
library(mapproj)
library(viridis)
library(knitr)
library(scales)
library(cowplot)
library(forcats)
library(ggpubr)
```

## Introduction

The goal of this project is to examine patterns in author diversity (gender/geographic) in coral reef publications over the past 15 years. We selected a range of peer-reviewed scientific journals across different impact factors and levels (incl. Conservation Letters, PNAS, Proceedings of the Royal Society B, Coral Reefs, PlosOne, Marine Policy, Marine Biology, Frontiers in Marine Science, Nature, Science). A team of global coral reef scientists reviewed these articles and extracted relevant data on research area, geography, authorship, and gender.

<span style="color: purple;">
**Notes for co-authors to consider are in bold purple**
</span>

```{r data, include=FALSE}
df2 <- readRDS("final_data_for_analysis_01302020.rds")
```

## Summary statistics

```{r include = FALSE}
n <- n_distinct(df2$Article.ID)
j <- unique(df2$Journal)
y <- c(min(df2$Pub_year):max(df2$Pub_year))
a <- unique(df2$Author)
c <- unique(df2$Country_affiliation)
```
This study considered ``r n`` unique studies published between ``r y[1]`` and ``r y[17]``.
This dataset represents works by ``r length(a)`` unique authors from ``r length(c)`` different countries 

<span style="color: purple;">
**The number of unique authors is going to be wrong as names were not standardized between databases). We need to decide whether we want to spend time cleaning this or not. Variations include Last,First; First Last; Last, First Initial**
</span>

```{r gg, fig.cap="**Figure 1.** Growth in coral reef publications over the last 15 years", echo=FALSE}
growth <- df2 %>% select(Article.ID,Pub_year) %>% distinct()
g <- count(growth,Pub_year)

gg <- ggplot(g, aes(Pub_year,n)) + 
  geom_col(fill="steelblue") +
  scale_x_continuous(breaks=seq(2003,2019,1), name="Publication year") +
  scale_y_continuous(breaks=seq(0,200,50), name="Number of articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1)
  )
  
plot(gg)
```
## Author characteristics (gender, diversity)

```{r gender, include=FALSE}
#Percent authors successfully identified and summary stats
authors <- df2 %>% select(Author_gender,Author) %>% distinct()
n_a <- n_distinct(authors$Author)
gender_stats <- count(authors,Author_gender)
```

This study found a maximum of ``r n_a`` unique authors in the evidence base. This number represents the maximum number of authors as different publication databases listed authors in different formats and thus we were unable to de-duplicate entries that were not an exact match (e.g. Last Name, First Name vs. Last Name, First Initial). ``r gender_stats[3,2]`` authors could not be located on the internet to confirm gender identity. Authors whose gender identity could not be reliably determined based on the presence of identified pronouns, declarations, or author(s) knowledge - were coded as "undetermined." The majority of authors in coral reef science are male.

```{r gender_stats, fig.cap='**Figure 2.** Gender distribution of authors in coral reef science', fig.width=5, echo=FALSE}
gs_plot <- filter(gender_stats,Author_gender != "Not found")
gs <- ggplot(gs_plot, aes(x="",y=n,fill=Author_gender)) +
  geom_bar(width=1, stat="identity") +
  scale_fill_brewer(palette="Accent") +
  theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid = element_blank(),
    legend.position='bottom') +
  geom_text(aes(y=n, label=percent(n/n_a)), size=3, position=position_stack(vjust=0.5)) +
  ylab("Number of authors") +
  guides(fill=guide_legend(title="Gender"))

plot(gs)
```


```{r gender_position, fig.cap='**Figure X.** Frequency of male vs. female authors in first, last, and all other author positions', echo=FALSE}
ratio <- df2 %>% select(Article.ID,Author_gender,First_last) %>% distinct()
x <- n_distinct(ratio$Article.ID)
rg <- count(ratio,Author_gender,First_last) %>% filter(First_last != "other")

ggplot(rg, aes(x=First_last,y=n)) +
  geom_bar(aes(fill=Author_gender), stat="identity", position=position_dodge()) +
  scale_fill_brewer(palette="Accent") +
  theme_minimal() +
  theme(
    axis.ticks.x = element_blank(),
    legend.position='right') +
  ylab("Number of articles") +
  xlab("Author position") +
  guides(fill=guide_legend(title="Gender"))
```

### Gender diversity trends
The following displays patterns in gender by looking at 4 metrics: author position (first, last), single author papers, and proportion of publication output contributed by men vs. women) across a number of different variables (publication year, country of affiliation, marine realm studied, study type, times cited, and journal).

<span style="color: purple;">
**Proportion of each gender's output was calculated by comparing the proportion of identified authorships for each gender in a given article. For example, if a paper had 9 authors, of which 8 were identified to gender, each authorship was granted an equal share of authorship (1/8 each). These fractions were then aggregated at different levels (e.g. countries, study_types, journals) to explore gender contributions. These reflect authorships and not individuals.**
</span>

```{r ge_data, include=FALSE}
##Summarize gender over different variables
##Remove undetermined and not found entries
gender_mf <- df2 %>% filter(Author_gender != "Undetermined" & Author_gender != "Not found")
```

### Trends over time

```{r gender_time, fig.cap='**Figure X.** Change in proportion of genders in first, last, and single author positions over time', echo=FALSE}
##Over time
#Proportion (overall male vs. female contribution)
gp_year <- gender_mf %>% select(Article.ID,Author_gender,Author,Pub_year,Prop_authorship) %>% distinct()
gpy <- aggregate(gp_year$Prop_authorship, by=list(Year=gp_year$Pub_year,Gender=gp_year$Author_gender), FUN=sum)

#Author position
gc_year <- gender_mf %>% select(Article.ID,Author_gender,First_last,Pub_year) %>% filter(First_last != "other") %>% distinct() %>% group_by(Pub_year,First_last)
gcy <- count(gc_year,Pub_year,Author_gender,First_last)

##Plotting
ggplot(gcy, aes(Pub_year,n)) + 
  geom_col(aes(fill=Author_gender),position=position_dodge()) +
  facet_grid(rows=vars(First_last), scales="free") +
  scale_x_continuous(breaks=seq(2003,2019,1), name="Publication year") +
  ylab("Number of articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    legend.position='bottom') +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

ggplot(gpy, aes(Year,x)) + 
  geom_col(aes(fill=Gender),position=position_dodge()) +
  scale_x_continuous(breaks=seq(2003,2019,1), name="Publication year") +
  scale_y_continuous(breaks=seq(0,120,10), name="Proportion of published articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1)
  ) +
  theme(
    legend.position='bottom') +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))
```

## Geographic distribution of research 

```{r cc, include=FALSE}
##Plot countries
#load in full country list
country <- read.csv("country_code_web.csv", head=TRUE, sep=",")
names(country) <- c("Study_country", "Code","Territory","Sovereignty")
country$Study_country <- as.character(country$Study_country)

##Count number of studies for all countries and arrange by region
country_count <- matrix(nrow=nrow(country), ncol=2)
rownames(country_count) <- country$Study_country
colnames(country_count) <- c("Study_country", "counts")

df_country <- df2 %>% select(Article.ID,Mapping_Country) %>% filter(!is.na(Mapping_Country)) %>% distinct()

#Calculate in for loop and write to blank matrix
for (c in country$Study_country){
  subset <- filter(df_country, Mapping_Country == c)
  country_count[c,1] <- c
  country_count[c,2] <- as.numeric(n_distinct(subset$Article.ID))
}
#Remove rownames and reformat data types
rownames(country_count) = NULL
country_count <- as.data.frame(country_count, stringsAsFactors=FALSE)
countries <- left_join(country,country_count,by="Study_country")

countries$counts <- as.numeric(countries$counts)
countries <- as.data.frame(countries)
countries_zero <- filter(countries, counts == 0)

countries <- arrange(countries,desc(counts))

map <- readShapeSpatial("TM_WORLD_BORDERS-0.3/TM_WORLD_BORDERS-0.3.shp")
map <- fortify(map, region="ISO3")

```

Research was conducted in ``r nrow(filter(countries, counts !=0 & Territory == "N"))+2`` countries and ``r nrow(filter(countries, counts !=0 & Territory == "Y"))`` territories. The most studied countries were ``r countries[1,1]`` (n=``r countries[1,5]``) and ``r countries[2,1]`` (n=``r countries[2,5]``). 

```{r cc_plot, fig.cap="**Figure 2.** Geographic distribution of study countries", fig.height=7, fig.width=12, echo=FALSE}
cc <- ggplot() + 
  geom_map(data=countries, aes(map_id=Code, fill=counts),map=map) + 
  geom_map(data=countries_zero, aes(map_id=Code),fill="#f0f0f0",map=map) + 
  expand_limits(x=map$long,y=map$lat) + 
  theme(panel.background = element_rect(fill = "grey50", colour = "white"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  scale_fill_gradient2(low="#deebf7",mid="#9ecae1",high="#08519c",midpoint=(max(countries$counts)/2),limits=c(0,max(countries$counts)))

plot(cc)
```

<span style="color: purple;">
**This one needs the legend to look nicer**
</span>

```{r cc_plot_alt, fig.cap='**Figure 2 (alternate).** Geographic distribution of study countries with discrete breaks', fig.height=7, fig.width=12, echo=FALSE}
##Define custom breaks for choropleth map
##Define custom breaks for choropleth map
min <- min(countries$counts) 
max <- max(countries$counts)
pretty_breaks <- c(5,25,50,100,250)
brks <- c(min,pretty_breaks,max)
#labels <- c("1-5","6-25","26-50","51-100","101-250","251-459")
labels <- c()
for(i in 1:length(brks)){
  labels <- c(labels,round(brks[i + 1], 2))
}
labels <- labels[1:length(labels)-1]

countries$brks2 <- cut(countries$counts,
                      breaks=brks,
                      include.lowest=TRUE,
                      labels=labels)

brks_scale <- levels(countries$brks2)
labels_scale <- brks_scale

cc <- ggplot() + 
  geom_map(data=countries, aes(map_id=Code, fill=brks2),map=map) + 
  geom_map(data=countries_zero, aes(map_id=Code),fill="#f0f0f0",map=map) + 
  expand_limits(x=map$long,y=map$lat) + 
  theme(panel.background = element_rect(fill = "grey50", colour = "white"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  coord_equal() +
  theme(legend.position = "bottom")


cd <- cc +
  scale_fill_manual(
    values=(brewer.pal(7, "BuGn")[2:7]),
    breaks=brks_scale,
    name="Number of articles",
    drop=FALSE,
    labels=labels_scale,
    guide=guide_legend(
      direction="horizontal",
      #keyheight= unit(2, units="mm"),
      #keywidth = unit(70/length(labels), units="mm"),
      title.position = "top",
      title.hjust = 0.5,
      label.hjust = 1,
      nrow=1,
      byrow=T,
      reverse=F,
      label.position="bottom"
      )
    )

plot(cd)
```

```{r gender_affil, fig.cap='**Figure X.** Gender distribution by country of affiliation. (A) First, last, and single author gender distribution for top two countries. (B) Proportion of authorship for top two countries. (C) First, last, and single, author gender distribution for all other countries. (D) Proportion of authorship for all other countries', fig.height=14, fig.width=12, echo=FALSE}
##By Country of Affiliation
#Proportion (overall male vs. female contribution)
gp_affil <- gender_mf %>% select(Article.ID,Author_gender,Author,Mapping_affiliation,Prop_authorship) %>% distinct()
gpa <- aggregate(gp_affil$Prop_authorship, by=list(Affiliation=gp_affil$Mapping_affiliation,Gender=gp_affil$Author_gender), FUN=sum) %>% mutate(Affiliation = fct_reorder(Affiliation, desc(x)))
gpa1 <- gpa %>% filter(Affiliation == "Australia" | Affiliation == "United States")
gpa2 <- gpa %>% filter(Affiliation != "Australia") %>% filter(Affiliation != "United States")

#Author position
gc_affil <- gender_mf %>% select(Article.ID,Author_gender,First_last,Mapping_affiliation) %>% filter(First_last != "other") %>% distinct()
gca <- count(gc_affil,Mapping_affiliation, Author_gender,First_last) %>% mutate(Mapping_affiliation = fct_reorder(Mapping_affiliation, desc(n)))
gca1 <- gca %>% filter(Mapping_affiliation == "Australia" | Mapping_affiliation == "United States")
gca2 <- gca %>% filter(Mapping_affiliation != "Australia") %>% filter(Mapping_affiliation != "United States")

##Plotting
a <- ggplot(gca1, aes(Mapping_affiliation,n)) + 
  geom_col(aes(fill=Author_gender),position=position_dodge())+
  facet_grid(rows=vars(First_last), scales="free") +
  scale_fill_brewer(palette = "Accent") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    axis.title.x=element_blank(),
    legend.position='bottom') +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

b <- ggplot(gpa1, aes(Affiliation,x)) + 
  geom_col(aes(fill=Gender)) +
  scale_y_continuous(breaks=seq(0,800,50)) +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    axis.title.x=element_blank(),
    legend.position='bottom') +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

c <- ggplot(gca2, aes(Mapping_affiliation,n)) + 
  geom_col(aes(fill=Author_gender),position=position_dodge())+
  facet_grid(rows=vars(First_last), scales="free") +
  scale_fill_brewer(palette = "Accent") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    axis.title.x=element_blank(),
    legend.position='bottom') +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

d <- ggplot(gpa2, aes(Affiliation,x)) + 
  geom_col(aes(fill=Gender)) +
  scale_y_continuous(breaks=seq(0,800,10)) +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    axis.title.x=element_blank(),
    legend.position='bottom') +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

fig_affil <- ggarrange(a,b,c,d,
          labels=c("A","B","C","D"),
          ncol=2, nrow=2,
          common.legend=TRUE,
          legend="bottom")

annotate_figure(fig_affil,
                left=text_grob("Number of articles", color="black",rot=90),
                bottom=text_grob("Country of affiliation", color="black"))
```

## Marine realms studied

```{r mar_region, include=FALSE}
#Plot marine realms
m_lyr <- readOGR(dsn="MEOW-TNC", layer="meow_ecos",verbose=FALSE)
m_lyr_fortified <- tidy(m_lyr,region="REALM")

##Plot countries
map_lyr <- readOGR(
  dsn="TM_WORLD_BORDERS-0.3",
  layer="TM_WORLD_BORDERS-0.3",
  verbose=FALSE
)

ggmap <- tidy(map_lyr,region="ISO3")

#Clean marine realm data
realm <- df2 %>% select(Article.ID,Marine_realm) %>% distinct() %>% filter(Marine_realm != "")
realm$Marine_realm <- gsub(", ",",", realm$Marine_realm)
realm$Marine_realm <- as.character(realm$Marine_realm)
m <- strsplit(realm$Marine_realm, split=",")
m_df <- data.frame(ID=rep(realm$Article.ID, sapply(m, length)), id = unlist(m))
colnames(m_df) <- c("Article.ID","id")
m_df <- distinct(m_df)

#Count studies per realm
marine_count <- count(m_df,id)
marine_count$id <- as.character(as.factor(marine_count$id))
marine_data <- m_lyr_fortified %>% left_join(marine_count, by="id")
marine_data$n[is.na(marine_data$n)] <- 0
marine_data_zero <- marine_data %>% filter(n == 0)
marine_data <- marine_data %>% filter(n != 0)

#Summarized in a table
marine_data_summary <- marine_data %>% select(id, n) %>% distinct() %>% arrange(desc(n))

```

```{r mar_region_plot, fig.cap='**Figure 3. Distribution of research effort over marine realms**', fig.height=7, fig.width=12, echo=FALSE, results='asis'}
ggplot() + 
  geom_polygon(data=marine_data, aes(fill=n,x=long,y=lat,group=group)) +
  geom_polygon(data=marine_data_zero, aes(x=long,y=lat,group=group), fill="#7c7c7c") +
  geom_polygon(data=ggmap, aes(x=long,y=lat,group=group), fill="#ffffff") +
  scale_fill_gradient2(low="#deebf7",mid="#9ecae1",high="#08519c") +
  theme_minimal() +
  theme(
    #text = element_text(family = "Ubuntu Regular", color = "#22211d"),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(color = "#ebebe5", size = 0.1),
    panel.grid.minor = element_blank(),
    plot.background = element_rect(fill = "#000000", color = NA), 
    panel.background = element_rect(fill = "#f5f5f2", color = NA), 
    legend.background = element_rect(fill = "#f5f5f2", color = NA),
    panel.border = element_blank()
  )


kable(marine_data_summary, caption="Total articles by marine realm")
```

```{r marine_realm_gender, echo=FALSE}
##By Marine Realm of Study
#Proportion (overall male vs. female contribution)
gp_marine <- gender_mf %>% select(Article.ID,Author_gender,Author,id,Prop_authorship) %>% filter(!is.na(id)) %>% filter(id != "Global") %>% filter(id != "Freshwater") %>% distinct()
gpm <- aggregate(gp_marine$Prop_authorship, by=list(Realm=gp_marine$id,Gender=gp_marine$Author_gender), FUN=sum) %>% mutate(Realm = fct_reorder(Realm, desc(x)))

#Author position
gc_marine <- gender_mf %>% select(Article.ID,Author_gender,First_last,id) %>% filter(First_last != "other") %>% filter(!is.na(id)) %>% filter(id != "Global") %>% filter(id != "Freshwater") %>% distinct()
gcm <- count(gc_marine,id,Author_gender,First_last) %>% mutate(id = fct_reorder(id, desc(n)))

##Plotting
ggplot(gcm, aes(id,n)) + 
  geom_col(aes(fill=Author_gender),position=position_dodge()) +
  facet_grid(rows=vars(First_last), scales="free") +
  ylab("Number of articles") +
  xlab("Marine realm studied") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    legend.position='bottom') +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

ggplot(gpm, aes(Realm,x)) + 
  geom_col(aes(fill=Gender)) +
  scale_y_continuous(breaks=seq(0,800,50), name="Proportion of published articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    legend.position='bottom') +
  xlab("Marine realm studied") +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))
```

## Research topics and study types

Research topics were wide-ranging.

<span style="color: purple;">
**Not even sure if this is useful, removed common words such as "coral*" and "reef*" to get a better picture of what about coral reefs was being studied. This is mapping the frequency of words (excluding stopwords) from the title and abstracts.**
</span>

```{r ta, include = FALSE}
#Create corpus of titles and abstracts
ta <- df2 %>% select(Article.ID,Title,Abstract) %>% distinct() %>% unite("Text",c("Title","Abstract"),sep="; ")
text <- ta$Text
docs <- Corpus(VectorSource(text))
#Clean corpus
docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("coral","corals","reefs","reef"))

#Create document-term-matrix
dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
wc <- data.frame(word = names(words),freq=words)
```

```{r ta_plot, fig.cap='**Figure X.** Wordcloud of frequent words appearing in titles and abstracts', echo=FALSE}
#Generate word cloud
set.seed(1234) 
wordcloud(words = wc$word, freq = wc$freq, min.freq = 10,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"), scale=c(2.5,0.25))

```

```{r st, include=FALSE, echo=FALSE}
###Types of studies
##What study types are encountered?
type <- df2 %>% select(Article.ID,Study_Type) %>% distinct()
type_count <- count(type,Study_Type) %>% arrange(desc(n))

st <- ggplot(type_count, aes(Study_Type,n)) + 
  geom_col(fill="steelblue") +
  scale_y_continuous(breaks=seq(0,1100,100), name="Number of articles") +
  xlab("Study type") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1)
  )

plot(st)
```

```{r study_gender, echo=FALSE}
##By study type
#Proportion (overall male vs. female contribution)
gp_study <- gender_mf %>% select(Article.ID,Author_gender,Author,Study_Type,Prop_authorship) %>% distinct()
gps <- aggregate(gp_study$Prop_authorship, by=list(Study_Type=gp_study$Study_Type,Gender=gp_study$Author_gender), FUN=sum) %>% mutate(Study_Type = fct_reorder(Study_Type, desc(x)))

#Author position
gc_study <- gender_mf %>% select(Article.ID,Author_gender,First_last,Study_Type) %>% filter(First_last != "other") %>% distinct()
gcs <- count(gc_study,Study_Type,Author_gender,First_last)
gcs <- rbind(gcs,c("Editorials/Correspondence","Female","single",0))
gcs <- rbind(gcs,c("Synthesis","Female","single",0))
gcs <- rbind(gcs,c("Undetermined","Female","single",0))
gcs$n <- as.integer(gcs$n)
gcs <- gcs %>% mutate(Study_Type = fct_reorder(Study_Type, desc(n)))

##Plotting
ggplot(gcs, aes(Study_Type,n)) + 
  geom_col(aes(fill=Author_gender),position=position_dodge()) +
  facet_grid(rows=vars(First_last), scales="free") +
  ylab("Number of articles") +
  xlab("Study type") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    legend.position='bottom') +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

ggplot(gps, aes(Study_Type,x)) + 
  geom_col(aes(fill=Gender)) +
  scale_y_continuous(breaks=seq(0,1100,50), name="Proportion of published articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    legend.position='bottom') +
  xlab("Study type") +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))
```

## Gender representation in examined journals

```{r journal_gender, echo=FALSE}
##By Journal
#Proportion (overall male vs. female contribution)
gender_mf$Journal[gender_mf$Journal == "PROCEEDINGS OF THE NATIONAL ACADEMY OF SCIENCES OF THE UNITED STATES OF AMERICA"] <- "PNAS"
gender_mf$Journal[gender_mf$Journal == "PROCEEDINGS OF THE ROYAL SOCIETY B-BIOLOGICAL SCIENCES"] <- "ProcB"
gender_mf$Journal[gender_mf$Journal == "MARINE ECOLOGY PROGRESS SERIES"] <- "MEPS"
gender_mf$Journal[gender_mf$Journal == "Plos One"] <- "PLoS One"

gp_journal <- gender_mf %>% select(Article.ID,Author_gender,Author,Journal,Prop_authorship) %>% distinct()
gpj <- aggregate(gp_journal$Prop_authorship, by=list(Journal=gp_journal$Journal,Gender=gp_journal$Author_gender), FUN=sum) %>% mutate(Journal = fct_reorder(Journal, desc(x)))

#Author position
gc_journal <- gender_mf %>% select(Article.ID,Author_gender,First_last,Journal) %>% filter(First_last != "other") %>% distinct()
gcj <- count(gc_journal,Journal,Author_gender,First_last) %>% mutate(Journal = fct_reorder(Journal, desc(n)))

##Plotting
ggplot(gcj, aes(Journal,n)) + 
  geom_col(aes(fill=Author_gender),position=position_dodge()) +
  facet_grid(rows=vars(First_last), scales="free") +
  ylab("Number of articles") +
  xlab("Journal") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    legend.position='bottom') +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))

ggplot(gpj, aes(Journal,x)) + 
  geom_col(aes(fill=Gender)) +
  scale_y_continuous(breaks=seq(0,1100,50), name="Proportion of published articles") +
  theme(
    axis.text.x=element_text(angle=45,hjust=1),
    legend.position='bottom') +
  xlab("Journal") +
  scale_fill_brewer(palette = "Accent") +
  guides(fill=guide_legend(title="Gender"),
         guide=guide_legend(
           direction="horizontal",
           #keyheight= unit(2, units="mm"),
           #keywidth = unit(70/length(labels), units="mm"),
           title.position = "top",
           title.hjust = 0.5,
           label.hjust = 1,
           label.position="bottom"
         ))
```

## Citation rates

```{r citation_gender, echo=FALSE, fig.cap='**Figure X.** How often papers authored by different total proportions of gender representation were cited'}
##Times Cited
#Proportion (overall male vs. female contribution)
gp_cite <- gender_mf %>% select(Article.ID,Author_gender,Author,Prop_authorship) %>% distinct()
gpc <- aggregate(gp_cite$Prop_authorship, by=list(Article.ID=gp_cite$Article.ID,Gender=gp_cite$Author_gender), FUN=sum) %>% arrange(Article.ID)
cite <- gender_mf %>% select(Article.ID,Times.Cited) %>% distinct() 
gpc <- left_join(gpc,cite,by="Article.ID")
gpc <- gpc %>% filter(Gender != "Male")

#Author position
gc_cite <- gender_mf %>% select(Article.ID,Author_gender,First_last,Times.Cited) %>% filter(First_last != "other") %>% distinct()
gcs <- count(gc_cite,Times.Cited,Author_gender,First_last)

##Plotting
ggplot(gpc, aes(x=x, y=Times.Cited)) +
  geom_point(size=1.5, color="#7FC97F", alpha=0.6,stroke=0.5) +
  scale_x_continuous(breaks=seq(0,1,0.1)) +
  scale_y_continuous(breaks=seq(0,2750,250)) +
  xlab("Proportion of female authorship (per article)") +
  ylab("Number of citations")
```
