---
title: "Carbon footprint setup"
author: "Emily Darling"
date: "02/10/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(here)
library(tidyverse)
library(janitor)
library(data.table)

```

# Load data and export a raw copy

First, we load the data prepared by Sam Cheng et al. from an RDS file. And make a distinct dataset with one row per study, affiliation country and study country

Filter to only first author

* Check with Sam if there's a more recent version of the data? 

```{r load-data}

#data in folder
df2 <- readRDS(here("final_data_for_analysis_01302020.rds")) %>% 
  as_tibble() %>% 
  clean_names()

df2
names(df2)

#choose only first author
df2 %>% 
  tabyl(first_last)

#choose only field studies
df2 %>% 
  tabyl(study_type_2)

#make dataset for carbon footprint analysis
#
data <- df2 %>% 
  filter(first_last == "first" & 
           study_type_2 == "Field-based") %>% 
  select(article_id, 
         title, 
         journal, 
         pub_year, 
         keywords, 
         abstract,
         #study_region, #NAs
         marine_realm, 
         times_cited, 
         doi, 
         study_type_2, 
         affiliation, 
         mapping_affiliation, 
         mapping_country) %>% 
  distinct()

#let's take only the most recent year to start (2018)
data %>% 
  filter(pub_year == 2018) %>% 
  fwrite(here("Carbon footprint", "data", 
              "2018-raw-data-from-Sam-01302020.csv"))

```

# Make country pairs 

How many country pairs are we talking about?

Pairs may be the same,eg., UK > Barbados and Barbados > UK

```{r country-pairs}
data %>% 
  filter(pub_year == 2018) %>% 
  select(contains("mapping")) %>% 
  distinct() %>% 
  na.omit() %>% 
  arrange(mapping_affiliation, 
          mapping_country)

.Last.value %>% 
  view()
  
  
```



